Cluster Paper

### 2015-03-30 ms.tex
wrote substructure section

\pdfoutput=1
\bibliographystyle{apj}
\citestyle{aa}

@@

\subsection{Structural Properties}
\editorial{Going to use the DS test along with a test for non-gaussian distributions of redshifts.}

>>>>

\bibliographystyle{apj}
\citestyle{aa}

@@

\subsection{Evidence of Substructure}
We leverage the large spectroscopic dataset to study the structural properties of the clusters. \cite{Pinkney1996} determine, from a comparison of five different methods that the Dressler-Shectman (DS) test \citep{Dressler1988} is the most sensitive to the presence of substructure.

The DS test, which combines the spatial positions and velocities of the galaxies, provides a method to locate substructure by identifying groups of galaxies which differ significantly from the cluster velocity distribution. Galaxy subsets are selected from a cluster of $n_{members}$ and each constituent galaxy deviation is calculated according to
\begin{equation}
	\delta_i^2 = \frac{N_{local}+1}{\sigma^2}\bigg{[}(\bar{v}_{local,i} - \bar{v})^2 + (\sigma_{local,i} - \sigma)^2\bigg{]}^2
\end{equation}
where $\bar{v}_{local}$ and $\sigma_{local}$ are the mean velocity and velocity dispersion for a subset of $N_{local}$ galaxies and $\bar{v}$ and $\sigma$ are the entire cluster's mean velocity and velocity dispersion. The choice of $N_{local}$ is left to the user. Originally, \cite{Dressler1988} choose $N_{local}=10$, however \cite{Bird1994} points out that using a fixed value for $N_{local}$ reduces the sensitivity to substructure. We follow \cite{Bird1994} in choosing $N_{local} = \sqrt n_{members}$. \editorial{doesn't talk about the nearest neighbors which is what we are using.}

The DS statistic is the $\Delta$-value given by, 
\begin{equation}
	\Delta = \sum^{n_{members}}_i \delta_i
\end{equation}
where a system is considered to contain substructure if $\Delta/n_{members} > 1$ \citep{Dressler1988}. A second method, described in \cite{Hou2012}, uses probabilities (P-values) rather than a threshold for the identification of substructure. P-values are computed by comparing the observed $\Delta$-value and the $Delta$-value after the velocities (but not positions) have been shuffled through a series of Monte Carlo runs. The probability of the existence of substructure becomes
\begin{equation}
	P = \sum (\Delta_{shuffled} > \Delta_{Observed}) / n_{shuffle}
\end{equation}
where $n_{shuffle}$ is the number of shufflings used. \editorial{This sounds a whole lot like the description given in Hou2012. Make sure that we aren't copying anything word for word. That'd be bad.}

In practice, we use locate the nearest neighbors using an unsupervised k-nearest neighbor algorithm as implemented in Scikit-Learn \citep{Pedregosa2012}.
